European or American? A re-examination of the transatlantic influence over the IMF

### 2025-07-25 manuscript/manuscript.qmd
Add contribution

>>>>

This paper addresses this gap by conducting a disaggregated, quantitative comparison of US and European influence on IMF lending outcomes. By distinguishing between the two major transatlantic actors, we provide new insights into the internal dynamics of power within the IMF and contribute to broader debates over institutional legitimacy, hegemony, and the geopolitics of economic governance.
